Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-09-25 nir_companions.tex
Pedros changes

    {\bl It is important to note that the search and detection of faint secondary spectra is not only relevant to planetary atmospheres, and has been attempted previously for the stellar and subtellar regime.} \citet{kolbl_detection_2015} developed a method to detect the presence of optical secondary spectra down to a flux ratio of 1 per cent in the hosts of \emph{Kepler} transit candidates. The presence of which can cause ambiguities in the system configuration, {\bl and introduce important systematics of the measured planet radius.} The characterization of the false positive probability rate for Kepler has been found to be as high as \(\sim\)35 per cent~\citet{santerne_sophie_2012},{\bl highlighting the strong incidence of the problem.}

@@

    The observations were conducted in service mode during period 89 under run ID.~089.C-0977(A) between April and \textbf{September} 2012. An observation is composed of 8 individual spectra each with an integration time of 180 seconds, observed in a ABBAABBA nod cycle pattern to obtain a high (>180) signal-to-noise when combined.

@@

    Each spectra was extracted twice using the \emph{rectangular} and \emph{optimal} extraction algorithms.
    The \emph{rectangular} extraction performs a rectangular aperture sum in the spatial direction while the \emph{optimal} extraction~\citep{horne_optimal_1986} also includes variance weighting to reduce the impact of the noise and deviant pixels on the total flux measurement. {The extracted nod-cycle spectra are normalized by dividing each by a polynomial fitted to the continuum.}

    The nod-cycle spectra were averaged to create a combined spectra with a higher signal-to-noise.
    Where possible the 8 optimally extracted spectra were combined, but several nod spectra were replaced with their rectangular counterparts because spectral artefacts were visually identified in the \emph{optimal} nod spectra. For the replacement nods, a iterative 4-\(\sigma\) rejection algorithm\footnote{Found at \url{https://github.com/jason-neal/nod_combination}} was applied to remove the bad pixels that were not removed in the \emph{rectangular} extraction.

@@

    Several parameters of the reduction pipeline were adjusted in an attempt to  remove these artefacts with limited success, e.g. the $\sigma$ rejection limits and the aperture width. In a small number of instances allowing the aperture width to be automatically adjusted removed the artefacts. These artefacts had not been observed with this pipeline in previous works in the \textit{H}-band, so these artefacts may have some wavelength dependence.

    The continuum normalization and nod combining steps were also performed with \textsc{iraf} while the following post reduction procedures and analysis utilize \textsc{python}. This pipeline was chosen over the ESO CRIRES pipeline because it was semi-automated, seemed relatively simple to use and, initial tests appeared to contain less bad pixel/cosmic ray artefacts in the extracted spectra compared to the ESO pipeline. In hindsight, the spectral artefacts observed decreased it's ease of use.

    \subsubsection{Wavelength calibration}
    \label{subsec:wave_cal}
    There is a known issue with the wavelength calibration from the CRIRES Th-Ar calibrations~\citep{kerber_laboratory_2009}, due to the low density of Th-Ar lines in the nIR and the alignment with the detectors narrow wavelength range (e.g.\ CRIRES-POP~\citep{nicholls_crirespop_2017}).
    Therefore, we use the telluric absorption lines present in each observation as the wavelength reference. Instead of directly using the HITRAN database~\citep{rothman_hitran2012_2013} for the line positions of the telluric spectra (e.g.~\citep{brogi_signature_2012,brogi_carbon_2014,dekok_detection_2013}), we use TAPAS atmospheric transmission models~\citep{bertaux_tapas_2014} obtained for each observation. These in turn use the HITRAN database but include atmospheric profiles and physical measurements to model the telluric absorption strength.

    The centroid of each telluric line is obtained by fitting the telluric transmission spectrum, \(T\), as a sum of Gaussian functions (subtracted from the continuum) representing the telluric lines,

@@

    The observed spectra contain thus two different components: the stellar and the telluric lines. {\bl Just like the telluric conmponets, the stellar spectra can be well approximated by a sum of Gaussian Functions. The observed spectra correspond to the product of the stellar and telluric components. The identification of telluric and stellar lines is done assuming the synthetic telluric models are complete and allow to identify all the telluric lines. The spectra can then be represented mathematically by} 
    \begin{align}
    I_{obs}(x) &= I_{tell}(x) \times {\bl I_{star}}(x) \nonumber \\
    I_{obs}(x) &= \Big(1 - {\Sigma}_{j}\ G(x, A_{j}, {\mu}_{j}, {\sigma}_{j})\Big) \times \Big(1 - {\Sigma}_{k} G(x, A_{k}, {\mu}_{k}, {\sigma}_{k})\Big), \label{eqn:obs}
    \end{align}

@@

    We attempted the technique suggested by~\citet{bertaux_tapas_2014} to address the poor \(\rm H_{2}O\) airmass scaling, to fit a scaling factor to the \(\rm {H}_{2}O\) absorption lines before convolution to the instrument resolution. This was achieved by first dividing the spectrum by a telluric model with only non-\(\rm H_{2}O\) constituents, convolved to the observed resolution, and scaled by the airmass to remove the non-\(\rm H_{2}O\) lines. Then a model with only \(\rm H_{2}O\) lines at full resolution was scaled by a factor \(\textrm{T}^{x}\), convolved to \(\rm R=50\,000\) and compared to the observed spectra. The factor \(x\) was fitted to find the best scaling factor for the \(\rm H_{2}O\) lines.

    This method corrected the deeper telluric lines well for a few spectra in our sample, but in many cases we found that the fitted scaling factor was affected by the presence of blended stellar lines (attempting to fit those also). It was also strongly influenced by the deepest \(H_{2}O\) telluric lines in the spectra analysed. We find that the telluric correction of the deep \(\rm H_{2}O\) lines could be improved with this technique, but, at the cost of worsening the correction of the many smaller \(\rm H_{2}O\) lines. Since the smaller \(\rm H_{2}O\) lines covered more of the spectrum in this region than the larger lines we chose not to continue with this separate \(\rm H_{2}O\) scaling. One possible solution for this would be to perform a piece-wise telluric correction, performing this step only for the deeper \( \rm H_{2}O\) lines, or by using one of the other tools that fits the telluric model to the observations. This technique could also benefit from a larger wavelength span that would enable blended lines to be ignored while having sufficient deep \(\rm H_{2}O\) lines to fit the scaling factor correctly. This small experiment shows that a simple scaling is not enough to correct for the absorption in an effective way, for this case.

@@

    \subsection{Tapas models}
    \label{subsec:tapas_models}
    We used telluric line models to wavelength calibrate the reduced spectra in Sect.~\ref{subsec:wave_cal} and to correct for the atmospheric absorption in Sect.~\ref{subsec:telluric_correction}. We utilized the TAPAS (Transmissions of the AtmosPhere for AStronomical data) web-service\footnote{\url{http://www.pole-ether.fr/tapas/}}~\citep{bertaux_tapas_2014} to obtain atmospheric transmission models for each observation. TAPAS uses the standard line-by-line radiation transfer model code LBLRTM~\citep{clough_linebyline_1995} along with the 2008 HITRAN spectroscopic database~\citep{rothman_hitran_2009} and Arletty atmospheric profiles derived using meteorological measurements from the ETHER data centre\footnote{\url{http://www.pole-ether.fr}}, which has a 6 hour resolution in atmospheric profiles.
    We use the mid-observation time to retrieve transmission models for each observation, with the Arletty atmospheric profiles\footnote{Nearest of the 6 hourly profiles} and vacuum wavelengths. The telluric models were retrieved without any barycentric correction to keep the telluric lines at a RV of zero with respect to the instrument. We obtained one model with all provided species present, convolved to a resolution of \(\rm R=50\,000\), and another two models without an instrumental profile convolution applied. For these two extra models, one contained only the transmission spectra of \(\rm H_{2}O\) while the other was for all other constituents except \(\rm H_{2}O\). This was to explore a known issue~\citep{bertaux_tapas_2014} with the depth of \(\rm H_{2}O\) absorption lines in Sect.~\ref{subsec:telluric_correction}.

    \subsection{Wavelength masking}
    Several wavelength masks are applied to remove wavelength regions from which we cannot extract spectral information.
    Firstly, regions near the edges of each detector where the wavelength solution is extrapolated outside of the calibrating telluric lines were removed, reducing the effective size of each detector by about \(10\) per cent or \(\sim\)100~pixels.

    Secondly, any remaining artefacts present in the spectra were masked out and the centres of deep telluric lines where telluric correction was not corrected properly. These sometimes resulted in ``emission-like'' peaks in the corrected spectrum. These two factors resulted in masking out around a further 10 per cent of the observed spectra.

    In Sect.~\ref{sec:results} a further wavelength restriction is used to mask out regions where there is a large mismatch between the observed spectrum and the closest synthetic spectra for the host star. This significantly restricts the wavelength span utilized to around only 43 per cent. The masked regions are shown as the shaded areas in Fig.~\ref{fig:visualinspection-hd2118471}.

    \section{Binary synthetic spectral recovery}
    \label{subsec:companion_recovery}
    We explore spectral fitting the observations with a binary model with the aim to detect the presence of the faint spectra which is in combination with the host star. The observed spectra are fitted with a binary combination of two synthetic spectral models, using \(\chi^{2}\) methods which have been extensively used in the literature~\citep[e.g.][]{astudillo-defru_harps_2015, passegger_fundamental_2016, zechmeister_spectrum_2018,nemravova_xtauri_2016}. {The parameters of the synthetic spectra fitted to the companion should provide an indication of the properties of the companion.}

    \subsection{Synthetic PHOENIX-ACES models}
    \label{subsec:spec_models}
    The PHOENIX-ACES synthetic spectra library~\citep{husser_new_2013} is used as the reference spectra to compose binary models for the spectral comparison. It uses the most recent version (16) of the PHOENIX code and is suitable for the spectra of cool stars. The full parameter space of the PHOENIX-ACES spectra is given in Table~\ref{tab:phoenix} but we restrict our usage to the domain covered by the observation targets.

@@

    The spectral model libraries were accessed using the useful ``grid tools'' interface provided in the \textsc{Starfish}\footnote{\url{https://github.com/iancze/Starfish}} \textsc{python} package~\citep{czekala_constructing_2015}, which made it efficient to load in the spectra when needed.

    The synthetic spectra are multiplied their wavelength to convert them into photon counts, ignoring multiplicative constants, as done in~\citet{figueira_radial_2016}\footnote{Synthetic models provide the spectral energy distribution (\(\rm erg\,s^{-1}\,cm^{2}\,cm^{-1}\)).}. The spectra are also convolved with a Gaussian kernel to match the resolution of the observations (\(\rm R=50\,000\)). Due to the distributive property of convolution it is efficient to apply convolution once to each synthetic spectra first, before the spectral pairs are combined.

    The PHOENIX-ACES models include dust in equilibrium with the gas phase while ignoring dust opacity and does not include any mixing/settling which is important for cooler BD atmospheres. They set a minimum library \(T_{\textrm{eff}}=2300\)~K to avoid the temperatures at which the modelling of clouds is necessary. This unfortunately limits the use of this library for this technique to the largest mass companions in our sample. For example a \(T_{\textrm{eff}}=2300\)~K corresponds to a BD with \(\rm M\sim84~M_{Jup}\) at 5 Gyr from the~\citet{baraffe_evolutionary_2003} evolutionary models.

@@

    The computed models are described in Sect.~\ref{models} and their output is interpolated to the wavelength grid of the observed spectra. The \(\chi^{2}\) is calculated by comparing the model and observation at each point. The results from all computed models is a multidimensional grid of \(\chi^2\) values for each combination of parameters, namely the spectral temperature, host RV, and companion RV for each detector, observation and target.

@@

    The inverse survival function of the \(\chi^2\) distribution is used to determine the confidence levels on the minimum \(\chi^2\) parameters. The inverse survival function returns a \(\Delta\chi^2\) value from the minimum \(\chi^2\) value for a given $sigma$-level and degree of freedom\footnote{In \textsc{python} with the \textsc{scipy} package this is a single line \texttt{scipy.stats.chi2(dof).isf(1-p)}, where \(p = 0.68\) for 1-\(\sigma\), and dof is the degree of freedom.}.
    For example, the \(\Delta \chi^2\) for a single degree of freedom required for the 1-, 2-, and 3-\(\sigma\) levels is 1, 4, and 9 respectively~\citep{bevington_data_2003}. This method assumes that the measured flux is observed with a SNR sufficiently high so that the noise on the spectrum is approximately Gaussian, and the \(\chi^2\) method appropriate.

@@

    \subsection{Computed model spectra}
    \label{models}
    \subsubsection{Single component model}
    \label{subsubsec:single-model}
    The single component model \(C^{1}_{i}\) comprises of a single synthetic spectrum, \(J\), (with model parameters \(T_{\textrm{eff}}\), logg, [Fe/H], [\(\alpha\)/Fe]) and is Doppler shifted by a RV value \({rv}_1\).

    It can be summarized by the equation, 
    \begin{equation}
    \rm C^{1}_{i}(\lambda) = J(\lambda_0(1-\frac{{rv}_1}{c})),
    \end{equation}

@@

    \subsubsection{Binary model}
    \label{subsubsec:binary-model}
    In the binary situation we consider the superposition of two synthetic spectral components, one each for the host and companion respectively. Both spectra are Doppler shifted by \({rv}_1\) which represents the RV motion of the host star, while the companion spectra is also Doppler shifted by a second RV, \({rv}_2\), representing the RV offset between the host and companion. In this way the mean motion of the system relative to Earth is captured only in \({rv}_1\). The two spectra are scaled by their squared radius (see Sect.~\ref{subsection-radius}) and then added together, thus fixing their relative amplitude.
    Given two spectral components \(J_{1}\) and \(J_{2}\) with radii \(R_1, R_2\) this equates to
    \begin{align}
    \rm C^{2}_{i}(\lambda) = &  J_{1}(\lambda_{0}(1 - \frac{rv_{1}}{c}))\times R_{1}^2 +\nonumber \\
    & J_{2}(\lambda_{0}(1-\frac{rv_{1}}{c})(1-\frac{rv_{2}}{c}))\times R_{2}^2
    \end{align}

    The continuum of the combined spectrum is fitted with an exponential and then normalized by dividing it by the fitted result as we assume we are in the Rayleigh-Jeans regime. This assumption is wavelength dependent and other appropriate continuum normalization techniques are also valid. In the case of a BD companion around an FGK star investigated here, the continuum is dominated by the contribution from the host star as it contributes the majority of the spectrum with flux ratios around 2110--2160~nm below \(\sim\)1 per cent.

@@

    The binary model should provide meaningful information about the companion parameters (e.g.\ \(T_{\textrm{eff}}\)) and a estimate of the flux ratio of the system. These can be combined with the~\citet{baraffe_evolutionary_2003} models to constrain the mass of the companion. However, we need to be careful with this model as the inclusion of extra spectral components and associated parameters could also provide a better fit to observations which do not have a companion, by fitting components of the noise.\\

    {The full list of grid parameters for the binary model are \(T_{\textrm{eff}}1\),  \(\rm logg_1\), [Fe/H]$_1$, [\(\alpha\)/Fe]$_1$, ${rv}_1$, \(T_{\textrm{eff}}2\), \(\rm logg_2\), [Fe/H]$_2$, [\(\alpha\)/Fe]$_2$, ${rv}_2$ where the subscripts 1 and 2 indicate the host and companion models respectively.}

    \subsubsection{Effective radius}
    \label{subsection-radius}
    To combine the two synthetic spectra with the correct observed flux ratio we need to integrate the emitted flux over the effective surface area of each emitting body respectively. Ignoring the common multiplicative constants that will disappear with normalization, we scale the two synthetic spectra individually by the square of their respective radii, \(R_1\) and \(R_2\).

    In this work we use the effective radius (PHXREFF keyword) of each component from the PHOENIX model headers. This is the radius used in modelling of the stellar atmospheres. We use this radii as it is directly tied to each model spectrum, and already available. The ratio of the radii from the two synthetic spectra in the binary models are provided in Table~\ref{tab:example_params}.

@@

    \subsection{Re-normalization}
    \label{subsec:renorm}
    Slight trends in the continuum level between the observed spectra and computed models were removed using the re-normalization following~\citep{passegger_fundamental_2016}:
    \begin{equation}
    F^{obs}_{re-norm} = F^{obs} \cdot \frac{\textrm{continuum fit}_{model}}{\textrm{continuum fit}_{observations}}.
    \end{equation}
    The polynomial continuum fits to the normalized observations and models are used to re-normalize the observed spectrum to the continuum of the models. For detectors 1--3 a polynomial of first degree was used, while for detector 4 a quadratic is needed to fit the edge of a strong Hydrogen line (Brackett-\(\gamma\)) at 2166~nm, which lies just off of detector 4. This broad line is only observed in the synthetic spectra and not in the reduced observations. It is assumed that this was normalized out during the reduction process.

    For each model we further allow the continuum level to be {\bl scaled between 0.95 and 1.05 as a free parameter} taking the model with the smallest \(\chi^2\) value.

    \subsection{Reducing parameters}
    \label{subsec:reduce-params}
    The high dimensionality of the binary model makes it computationally challenging and difficult to analyse the \(\chi^2\) space.
    For reference, the multiplicative parameter space is squared when increasing from one spectral component in the single model to a binary model, and becomes computationally expensive. In general the number of possible parameter combinations for \(c\) spectral components each with a grid of \(m\) models increases to \(c^m\). If the full set of PHOENIX-ACES library spectra (66456) is explored with a binary fit then this naively balloons to over 4.4 billion possible combinations. Half of these are not unique as the host and companion components are swapped. This is the worst case scenario and we implement a number of assumptions to vastly reduce the parameter-space enabling faster computation.

    Our first assumption is to restrict ourselves to models with an Alpha element abundance ([\(\alpha\)/Fe]) of zero. This is likely a very good approximation as all our targets have solar metallicity and are thus very likely to belong to the thin disk of the Galaxy, where [\(\alpha\)/Fe] values are close to zero (i.e., solar) -- e.g.~\citet{adibekyan_chemical_2012}. Our second assumption is that the search space can be significantly reduced using the literature values for the host star given in Table~\ref{tab:starparams}. The metallicity of both components and the logg of the host star is fixed to the grid points closest to the literature values. The uncertainties on the literature measurements for metallicity (\(\sim\)0.05) and logg (\(\sim\)0.1) are both smaller than the grid steps of 0.5 for these parameters.
    For the logg of the companion the~\citet{baraffe_evolutionary_2003,baraffe_new_2015} evolutionary model value are used for the given companions \(\textrm{M}_2\)/\(\textrm{M}_2\sin{i}\) and hosts age.

>>>>

    {\bl It is important to note that the search and detection of faint secondary spectra is not only relevant to planetary atmospheres, and has been attempted previously for the stellar and substellar regime.} \citet{kolbl_detection_2015} developed a method to detect the presence of optical secondary spectra down to a flux ratio of 1 per cent in the hosts of \emph{Kepler} transit candidates. The presence of which can cause ambiguities in the system configuration, {\bl and introduce important systematics of the measured planet radius.} The characterization of the false positive probability rate for Kepler has been found to be as high as \(\sim\)35 per cent~\citet{santerne_sophie_2012},{\bl highlighting the strong incidence of the problem.}

@@

    The observations were conducted in service mode during period 89 under run ID.~089.C-0977(A) between April and September 2012. An observation is composed of 8 individual spectra each with an integration time of 180 seconds, observed in a ABBAABBA nod cycle pattern to obtain a high (>180) signal-to-noise when combined.

@@

    Each spectra was extracted twice using the \emph{rectangular} and \emph{optimal} extraction algorithms.
    The \emph{rectangular} extraction performs a rectangular aperture sum in the spatial direction while the \emph{optimal} extraction~\citep{horne_optimal_1986} also includes variance weighting to reduce the impact of the noise and deviant pixels on the total flux measurement. {\bl The extracted nod-cycle spectra are continuum-normalized by division by a polynomial fit.}

    The average of the 8 nod-cycle spectra was used to create a combined spectra with a higher signal-to-noise.
    {\bl By default, the 8 optimally extracted spectra were used to create the combined spectra. However, on some observations spectral artefacts were visually identified in the \emph{optimal} nod spectra. Several parameters of the reduction pipeline (e.g. the $\sigma$ rejection limits and the aperture width) were adjusted in an attempt to remove these artefacts, but with limited success.
    To consistently remove these artefacts, in the affected exposures the nod spectra were replaced with their rectangular extraction equivalents. Since in a rectangular extraction the bad pixels are not flagged and removed, a iterative 4-\(\sigma\) rejection algorithm\footnote{Found at \url{https://github.com/jason-neal/nod_combination}} was applied.}

@@

    These artefacts had not been observed in previous works using this pipeline in the \textit{H}-band, so this {\bl can be a wavelength-dependent affect. Alternatively, it can be an effect only affecting observations taken in some periods. The data gathered does not allow us to reach a conclusion.}

    The continuum normalization and nod combining steps were performed with \textsc{iraf} while the following post reduction procedures and analysis utilize \textsc{python}. This pipeline was chosen over the ESO CRIRES pipeline because it was semi-automated, seemed relatively simple to use and, initial tests appeared to contain less bad pixel/cosmic ray artefacts in the extracted spectra compared to the ESO pipeline. In hindsight, the spectral artefacts observed decreased it's ease of use.

    \subsubsection{Wavelength calibration}
    \label{subsec:wave_cal}
    {\bl Wavelength calibration of CRIRES data using Th-Ar hollow-cathode lamps is affected by important limitations~\citep{kerber_laboratory_2009}. The low density of Th-Ar lines in the nIR and the detectors narrow wavelength range (e.g.\ CRIRES-POP~\citep{nicholls_crirespop_2017}) lead to a very low number of lines for defining a wavelength solution.}
    Therefore, we use the telluric absorption lines present in each observed spectra as the wavelength reference. Instead of directly using the HITRAN database~\citep{rothman_hitran2012_2013} for the line positions of the telluric spectra (e.g.~\citep{brogi_signature_2012,brogi_carbon_2014,dekok_detection_2013}),{\bl we use the TAPAS atmospheric transmission models~\citep{bertaux_tapas_2014} to simulate the telluric lines present on each observation.} These in turn use the HITRAN database, but include atmospheric profiles and physical measurements to model the telluric absorption strength.

    The centroid of each telluric line is obtained by fitting the telluric transmission spectrum, \(T\), as a sum of Gaussian functions representing{\bl the individual} telluric lines,

@@

    The observed spectra contain thus two different components: the stellar and the telluric lines. {\bl Just like the telluric components, the stellar spectra can be well approximated by a sum of Gaussian Functions. The observed spectra correspond to the product of the stellar and telluric components. The identification of telluric and stellar lines is done assuming the synthetic telluric models are complete and allow to identify all the telluric lines. The spectra can then be represented mathematically by} 
    \begin{align}
    I_{obs}(x) &= I_{tell}(x) \times {\bl I_{star}}(x) \nonumber \\
    I_{obs}(x) &= \Big(1 - {\Sigma}_{j}\ G(x, A_{j}, {\mu}_{j}, {\sigma}_{j})\Big) \times \Big(1 - {\Sigma}_{k} G(x, A_{k}, {\mu}_{k}, {\sigma}_{k})\Big), \label{eqn:obs}
    \end{align}

@@

    The TAPAS (Transmissions of the AtmosPhere for AStronomical data) web-service\footnote{\url{http://www.pole-ether.fr/tapas/}}~\citep{bertaux_tapas_2014} was used to obtain atmospheric transmission models for each observation. TAPAS uses the standard line-by-line radiation transfer model code LBLRTM~\citep{clough_linebyline_1995} along with the 2008 HITRAN spectroscopic database~\citep{rothman_hitran_2009} and Arletty atmospheric profiles derived using meteorological measurements from the ETHER data centre\footnote{\url{http://www.pole-ether.fr}}, which has a 6 hour resolution in atmospheric profiles.
    We use the mid-observation time to retrieve transmission models for each observation, with the Arletty atmospheric profiles\footnote{Nearest of the 6 hourly profiles} and vacuum wavelengths. The telluric models were retrieved without any barycentric correction to keep the telluric lines at a RV of zero with respect to the instrument. We obtained one model with all provided species present, convolved to a resolution of \(\rm R=50\,000\), and another two models without an instrumental profile convolution applied. For these two extra models, one contained only the transmission spectra of \(\rm H_{2}O\) while the other was for all other constituents except \(\rm H_{2}O\).

    Before the correction, the depth of the telluric lines were re-scaled to match the airmass of the observation using the relation \(\rm T = T^{\beta}\), where \(\rm T\) is the telluric spectrum and \(\beta\) is the airmass ratio between the observation and model. This changed the depth of most absorption lines to match the observations, but does not correctly scale the deeper \(\rm H_{2}O\) lines. The scaled telluric model is interpolated to the wavelengths of the observed spectrum and then used to correct the observed spectra. An example of a telluric corrected spectra is shown in the middle panel of Fig.~\ref{fig:spectral_example}, with the light blue shading indicating where the deeper telluric lines were.

    {\bl We attempted the technique suggested by~\citet{bertaux_tapas_2014} of fitting a scaling factor to the \(\rm {H}_{2}O\) absorption lines before convolution to the instrument resolution as a way to address the poor \(\rm H_{2}O\) airmass scaling.} This was achieved by first dividing the spectrum by a telluric model with only non-\(\rm H_{2}O\) constituents, convolved to the observed resolution, and scaled by the airmass to remove the non-\(\rm H_{2}O\) lines. Then a model with only \(\rm H_{2}O\) lines at full resolution was scaled by a factor \(\textrm{T}^{x}\), convolved to \(\rm R=50\,000\) and compared to the observed spectra. The factor \(x\) was fitted to find the best scaling factor for the \(\rm H_{2}O\) lines.

    This method corrected the deeper telluric lines in a satisfactory way for some spectra in our sample, but in many cases we found that the fitted scaling factor was affected by the presence of blended stellar lines (attempting to fit those also) and dominated by the deepest \(H_{2}O\) telluric lines in the spectra analysed. We find that the telluric correction of the deep \(\rm H_{2}O\) lines could be improved with this technique, but, at the cost of worsening the correction of the many smaller \(\rm H_{2}O\) lines. Since the smaller \(\rm H_{2}O\) lines covered a wider wavelength range of the spectrum than the larger lines we chose not to continue with this separate \(\rm H_{2}O\) scaling. One possible solution for this would be to perform a piece-wise telluric correction, performing this step only for the deeper \( \rm H_{2}O\) lines, or by using one of the other tools that fits the telluric model to the observations. This technique could also benefit from a larger wavelength span that would enable blended lines to be ignored while having sufficient deep \(\rm H_{2}O\) lines to fit the scaling factor correctly. This small experiment shows that for cases like ours a simple scaling is not enough to correct for the absorption in an effective way.

@@

    \subsection{Wavelength masking}
    {\bl Poor wavelength calibration, the blending of stellar lines, and the imperfect telluric correction led to several wavelength regions being unusable to extract wavelength information, and these were masked in the subsequent analysis.}
    Firstly, we removed regions near the edges of each detector where the wavelength solution is extrapolated outside the calibrating telluric lines region. This reduced the effective size of each detector by about \(10\) per cent or \(\sim\)100~pixels.

    Secondly, any remaining artefacts present and the centres of deep telluric lines where telluric correction was not corrected properly were masked out. These sometimes resulted in ``emission-like'' peaks in the corrected spectrum. These two factors led to masking out a further 10 per cent of the observed spectra.

    As seen in Sect.~\ref{sec:results} a further wavelength restriction leads to mask out regions where there is a large mismatch between the observed spectrum and the closest synthetic spectra for the host star. This significantly restricts the wavelength span utilized to around only 43 per cent. The masked regions are shown as the shaded areas in Fig.~\ref{fig:visualinspection-hd2118471}.

    \section{Binary synthetic spectral recovery}
    \label{sec:companion_recovery}
    {\bl On the reduced, wavelength-calibrated and telluric-corrected spectra we attempt a spectral fitting of a binary model with the aim of detecting the presence of the faint spectra of the companion superimposed to that of the host star. The matching is done using \(\chi^{2}\) methods which have been extensively used in the literature~\citep[e.g.][]{astudillo-defru_harps_2015, passegger_fundamental_2016, zechmeister_spectrum_2018,nemravova_xtauri_2016}.}

    \subsection{Synthetic PHOENIX-ACES models}
    \label{subsec:spec_models}
    The binary models were created using PHOENIX-ACES synthetic spectra library~\citep{husser_new_2013}. It uses the most recent version (16) of the PHOENIX code and is suitable to reproduce the spectra of cool stars. The full parameter space of the PHOENIX-ACES spectra is given in Table~\ref{tab:phoenix}, but we restrict our usage to the domain covered by the observation targets.

@@

    The spectral model libraries were accessed using the ``grid tools'' interface provided in the \textsc{Starfish}\footnote{\url{https://github.com/iancze/Starfish}} \textsc{python} package~\citep{czekala_constructing_2015}.

    The synthetic spectra are multiplied by their wavelength to convert them into photon counts, ignoring multiplicative constants, as done in~\citet{figueira_radial_2016}\footnote{Synthetic models provide the spectral energy distribution (\(\rm erg\,s^{-1}\,cm^{2}\,cm^{-1}\)).}. The spectra are also convolved with a Gaussian kernel to match the resolution of the observations (\(\rm R=50\,000\)). Due to the distributive property of convolution it is more efficient to apply convolution once to each synthetic spectra first, before the spectral pairs are combined.

    The PHOENIX-ACES models include dust in equilibrium with the gas phase while ignoring dust opacity and not including any mixing/settling. They set a minimum library \(T_{\textrm{eff}}=2300\)~K to avoid the temperatures at which the modelling of clouds is necessary. This unfortunately limits the use of this library for this technique to the most massive mass companions in our sample. For example a \(T_{\textrm{eff}}=2300\)~K corresponds to a BD with \(\rm M\sim84~M_{Jup}\) at 5 Gyr from the~\citet{baraffe_evolutionary_2003} evolutionary models.

@@

    The computed models are are interpolated to the wavelength grid of the observed spectra. The \(\chi^{2}\) is calculated by comparing the model and observation on their common wavelength grid. The results from all computed models is a multidimensional grid of \(\chi^2\) values for each combination of parameters, namely the spectral temperature, host RV, and companion RV for each detector, observation and target.

@@

    The inverse survival function of the \(\chi^2\) distribution is used to determine the confidence levels on the minimum \(\chi^2\) parameters. The inverse survival function returns a \(\Delta\chi^2\) value from the minimum \(\chi^2\) value for a given sigma level and degree of freedom.
    For example, the \(\Delta \chi^2\) for a single degree of freedom required for the 1-, 2-, and 3-\(\sigma\) levels is 1, 4, and 9 respectively~\citep{bevington_data_2003}. This method assumes that the measured flux is observed with a SNR sufficiently high so that the noise on the spectrum is approximately Gaussian, and as such the \(\chi^2\) method appropriate.

@@

    \subsection{Computed model spectra}
    \label{models}
    \subsubsection{Single component model}
    \label{subsubsec:single-model}
    The single component model \(C^{1}_{i}\) is comprised of a single synthetic spectrum, \(J\), (with model parameters \(T_{\textrm{eff}}\), logg, [Fe/H], [\(\alpha\)/Fe]), Doppler shifted by an RV of value \({rv}_1\).

    It can be represented by the equation, 
    \begin{equation}
    \rm C^{1}_{i}(\lambda) = J(\lambda_0(1-\frac{{rv}_1}{c})),
    \end{equation}

@@

    \subsubsection{Binary model}
    \label{subsubsec:binary-model}
    {\bl We consider also the case of} the superposition of two synthetic spectral components, for the host and the companion. Both spectra are Doppler shifted by \({rv}_1\), which represents the RV motion of the host star, while the companion spectra is also Doppler shifted by a second RV, \({rv}_2\), representing the RV offset between the host and companion. In this way the mean motion of the system relative to Earth is \({rv}_1\). The two spectra are scaled by their squared radius (see Sect.~\ref{subsection-radius}) and then added together, thus fixing their relative amplitude.
    Given two spectral components \(J_{1}\) and \(J_{2}\) with radii \(R_1, R_2\) this{\bl translates} to
    \begin{align}
    \rm C^{2}_{i}(\lambda) = &  J_{1}(\lambda_{0}(1 - \frac{rv_{1}}{c}))\times R_{1}^2 +\nonumber \\
    & J_{2}(\lambda_{0}(1-\frac{rv_{1}}{c})(1-\frac{rv_{2}}{c}))\times R_{2}^2
    \end{align}

    In the case of a BD companion around an FGK star investigated here, the continuum is dominated by the contribution from the host star as it contributes the majority of the spectrum with flux ratios below \(\sim\)1 per cent for the 2110--2160~nm wavelength range. {\bl Since we are in the Rayleigh-Jeans regime for the star, that dominates the emission, the continuum of the combined spectrum is fitted and normalized using an exponential.}

@@

    {\bl The full list of grid parameters for the binary model are \(T_{\textrm{eff}}1\),  \(\rm logg_1\), [Fe/H]$_1$, [\(\alpha\)/Fe]$_1$, ${rv}_1$, \(T_{\textrm{eff}}2\), \(\rm logg_2\), [Fe/H]$_2$, [\(\alpha\)/Fe]$_2$, ${rv}_2$ where the subscripts 1 and 2 indicate the host and companion models respectively.}

    \subsubsection{Effective radius}
    \label{subsection-radius}
    To combine the two synthetic spectra with the observed flux ratio we need to integrate the emitted flux over the effective surface area of each emitting body. Ignoring the common multiplicative constants that will disappear with normalization, we scale the two synthetic spectra individually by the square of their respective radii, \(R_1\) and \(R_2\).

    In this work we use the effective radius (PHXREFF keyword) of each component from the PHOENIX model headers. This is the radius used in modelling of the stellar atmospheres. The ratio of the radii from the two synthetic spectra in the binary models are provided in Table~\ref{tab:example_params}.

@@

    \subsection{Re-normalization}
    \label{subsec:renorm}
    {\bl Remaining} trends in the continuum level between the observed spectra and computed models were removed using the re-normalization following~\citep{passegger_fundamental_2016}:
    \begin{equation}
    F^{obs}_{re-norm} = F^{obs} \cdot \frac{\textrm{continuum fit}_{model}}{\textrm{continuum fit}_{observations}}.
    \end{equation}
    For detectors 1--3 a polynomial of first degree was used, while for detector 4 a quadratic function was used to fit the edge of a strong Hydrogen line (Brackett-\(\gamma\)) at 2166~nm, which lies just off of detector 4. This broad line is only observed in the synthetic spectra and not in the reduced observations. It is assumed that this was normalized out during the reduction process.

    For each model we further allow the continuum level to be {\bl scaled with a factor between 0.95 and 1.05} and choose the model with the smallest \(\chi^2\) value.

    \subsection{Reducing the parameter space}
    \label{subsec:reduce-params}
    The high dimensionality of the binary model makes it computationally challenging and difficult to analyse the \(\chi^2\) space.
    For reference, the multiplicative parameter space is squared when increasing from one spectral component in the single model to a binary model, and therefore becomes computationally expensive. In general the number of possible parameter combinations for \(c\) spectral components each with a grid of \(m\) models increases to \(c^m\). If the full set of PHOENIX-ACES library spectra (66456) is explored with a binary fit then this naively balloons to over 4.4 billion possible combinations. Half of these are not unique as the host and companion components are swapped. This is the worst case scenario and we implement a number of assumptions to vastly reduce the parameter-space enabling faster computation.

    Our first assumption is to restrict ourselves to models with an Alpha element abundance ([\(\alpha\)/Fe]) of zero. This is in all likelihood a very good approximation as all our targets have solar metallicity and are thus very likely to belong to the thin disk of the Galaxy, where [\(\alpha\)/Fe] values are close to zero (i.e., solar) -- e.g.~\citet{adibekyan_chemical_2012}. Our second{\bl step in simplifying the problem is assuming literature values for the host star metallicity and surface gravity given in Table~\ref{tab:starparams}}. The metallicity of both components and the logg of the host star is fixed to the grid points closest to the literature values. The uncertainties on the literature measurements for metallicity (\(\sim\)0.05) and logg (\(\sim\)0.1) are both smaller than the grid steps of 0.5 used for these parameters.
    For the logg of the companion the~\citet{baraffe_evolutionary_2003, baraffe_new_2015} evolutionary model value are used for the given companions \(\textrm{M}_2\)/\(\textrm{M}_2\sin{i}\) and hosts age.
